---
title: "theCLT"
author: "Alex Moreno"
date: 'Summer 2022'
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(lattice)
data("imagpop")
```

```{r}
KK_data <- imagpop$kkardashtemp
my1000 <- sample(KK_data, size = 1000, replace=T)
densityplot(my1000,main="original data")
print(mean(KK_data))
print(sd(KK_data))
```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

Not unimodal because there are multiple peaks. It is bimodal. 

Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")
print(mean(x.avg))
print(sd(x.avg))
```


Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

It is not unimodal becuase there are multiple peaks.
Trimodal graph. Highest peak is the center curve. Mean is 50.47. Standard deviation is 29.65.

Do this again for 4 random samples

```{r}
numb = 4
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
x.std <- apply(mdata,1, sd)

KKmean = mean(x.avg)
KKstd = sd(x.std)

print(mean(x.avg))
print(sd(x.avg))

densityplot(x.avg,main="sample size 4")
```

Trimodal graph. Highest is the middle one. 

Then again for 9 random samples

```{r}
numb = 9
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
x.std <- apply(mdata,1, sd)

KKmean = mean(x.avg)
KKstd = sd(x.std)

print(mean(x.avg))
print(sd(x.avg))

densityplot(x.avg,main="sample size 9")
```

then 16 random samples

```{r}
numb = 16
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
x.std <- apply(mdata,1, sd)

KKmean = mean(x.avg)
KKstd = sd(x.std)

print(mean(x.avg))
print(sd(x.avg))

densityplot(x.avg,main="sample size 16")
```

finally for 36 random samples.

```{r}
numb = 36
Kdata   <- sample(KK_data, size = numb*1000, replace=T)
mdata  <-matrix(Kdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
x.std <- apply(mdata,1, sd)

KKmean = mean(x.avg)
KKstd = sd(x.std)

print(mean(x.avg))
print(sd(x.avg))

densityplot(x.avg,main="sample size 36")
```

Bimodal graph. The mean is 50.58. Standard deviation is 6.864. Almost all the samples are insidee the center of the graph curve.


Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

Be sure to comment on both the mean and standard deviation of the sample averages - the CLT makes a statement about what to expect from both.

 

Then submit the link to your github project  to canvas to complete this assignment.